---
title: "PA1_template"
author: "jdelgastat"
date: "Monday, June 09, 2014"
output: html_document
---

##### 1 Loading the data

```{r}
activity <- read.table(file = "activity.csv", header = T, sep = ",", colClasses = c("numeric", "Date", "factor"))
```

##### 2 Histogram of number of steps taken each day
```{r}
hist(x = activity$steps, breaks = 50, main = "total number of steps taken each day", xlab = "Steps", col = "lightblue")
```

##### 3 Mean of number of steps taken per day
```{r}
meansteps <- mean(activity$steps, na.rm = T)
```
The mean of steps taken per day is `r meansteps` steps.

##### 4 Median of number of steps taken per day
```{r}
mediansteps <- median(activity$steps, na.rm = T)
```
The median of steps taken per day is `r mediansteps` steps.

##### 5 Time series plot of the 5-minute interval and the average number of steps taken, averaged across all days
```{r}
activity_clean <- na.omit(object = activity)
mean_steps_by_interval <- as.numeric(lapply(split(x = activity_clean$steps, f = activity_clean$interval), mean))
plot(mean_steps_by_interval, type = "l", xlab = "5 minutes interval", ylab = "Mean of steps across all days", main = "Average number of steps by 5 minutes interval" )
```

##### 6 Five minute interval with maximum number of steps across all the days
```{r}
intervals <- sort(as.numeric(levels(activity$interval)))
maxinterval <- data.frame(intervals, mean_steps_by_interval)
max <- maxinterval[(mean_steps_by_interval == max(maxinterval$mean_steps_by_interval)), ]
maximo <- as.character(max[[1]])
h <- substr(x = maximo, start = 1, stop = 2)
m <- substr(x = maximo, start = 3, stop = 4)
hm <- paste(h, ":", m, sep = "")
```
The 5 minutes interval with maximum number of steps across all the days begins at `r hm`.

##### 7 The total number of rows with missing values in the dataset
```{r}
rowsNA <- nrow(activity) - nrow(activity_clean)
```
The total number of rows with missing values in the dataset is `r rowsNA` rows.


##### 8 Devise a strategy for filling in all of the missing values in the dataset





##### 9 New dataset that is equal to the original dataset but with the missing data filled in




##### 10 Histogram of the total number of steps taken each day and Calculate and report the mean and median total number of steps taken per day





##### 11 New factor variable in the dataset with two levels - "weekday" and "weekend" indicating whether a given date is a weekday or weekend day







##### 12 Panel plot containing a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all weekday days or weekend days (y-axis)






